\documentclass[12pt]{../style-files/ociamthesis}

\usepackage{amssymb}
\usepackage{titlesec}
\usepackage{amsmath}
\usepackage{float}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subfig}
\usepackage{xcolor}
\usepackage[section]{placeins}
\usepackage{mathrsfs}
\usepackage{bm}
\usepackage{stmaryrd}
\usepackage{siunitx}
\usepackage{rotating}
\usepackage[utf8]{inputenc}
\usepackage[round]{natbib}

\usepackage{geometry}
 \geometry{
 a4paper,
 left=40mm,
 right=30mm,
 top=30mm,
 bottom=30mm
 }

\definecolor{theblue}{HTML}{0000CD}

% disable this package for printed version
\usepackage[colorlinks=true, linktocpage=true, allcolors=theblue]{hyperref}

\titleformat{\chapter}[display]
  {\bfseries\Large}
  {\filright\MakeUppercase{\chaptertitlename} \Large\thechapter}
  {1ex}
  {}
  [\vspace{1ex} \hrule \vspace{1pt} \hrule]

\newcommand{\adv}{    {\it Adv. Space Res.}} 
\newcommand{\annG}{   {\it Ann. Geophys.}} 
\newcommand{\aap}{    {\it Astron. Astrophys.}}
\newcommand{\aaps}{   {\it Astron. Astrophys. Suppl.}}
\newcommand{\aapr}{   {\it Astron. Astrophys. Rev.}}
\newcommand{\ag}{     {\it Ann. Geophys.}}
\newcommand{\aj}{     {\it Astron. J.}} 
\newcommand{\apj}{    {\it Astrophys. J.}}
\newcommand{\apjl}{   {\it Astrophys. J. Lett.}}
\newcommand{\apss}{   {\it Astrophys. Space Sci.}} 
\newcommand{\cjaa}{   {\it Chin. J. Astron. Astrophys.}} 
\newcommand{\gafd}{   {\it Geophys. Astrophys. Fluid Dyn.}}
\newcommand{\grl}{    {\it Geophys. Res. Lett.}}
\newcommand{\ijga}{   {\it Int. J. Geomagn. Aeron.}}
\newcommand{\jastp}{  {\it J. Atmos. Solar-Terr. Phys.}} 
\newcommand{\jgr}{    {\it J. Geophys. Res.}}
\newcommand{\mnras}{  {\it Mon. Not. Roy. Astron. Soc.}}
\newcommand{\na}{     {\it New Astronomy}}
\newcommand{\nat}{    {\it Nature}}
\newcommand{\pasp}{   {\it Pub. Astron. Soc. Pac.}}
\newcommand{\pasj}{   {\it Pub. Astron. Soc. Japan}}
\newcommand{\pre}{    {\it Phys. Rev. E}}
\newcommand{\solphys}{{\it Solar Phys.}}
\newcommand{\sovast}{ {\it Soviet  Astron.}} 
\newcommand{\ssr}{    {\it Space Sci. Rev.}}
\newcommand{\caa}{    {\it Chinese Astron. Astrohpys.}} 
\newcommand{\apjs}{   {\it Astrophys. J. Suppl.}}

\begin{document}

\baselineskip=18pt

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

\newcommand{\bv}{\mathbf{v}}
\newcommand{\bB}{\mathbf{B}}


%------------------------------------------------------------------------------
\chapter{Introduction}
\label{chap:intro}
%------------------------------------------------------------------------------

%------------------------------------------------------------------------------
\section{The Sun}
\label{sec: sun}
%------------------------------------------------------------------------------

Its significance, structure, and magnetic phenomena.

From my confirmation report:
\textit{The Sun is hot. So hot, in fact, that many of the constituent particles cannot form
	neutral atoms, but exist as a soup of negatively charged electrons and positively
	charged nuclei. Matter in this state is known as plasma. Because many of the charges
	are dissociated in a plasma, it can conduct electricity and therefore induce a magnetic
	field. This magnetic field can interact with the fluid to produce a nonlinear coupling
	between the magnetic field and the plasma motion. This coupling is described by
	magnetohydrodynamic (MHD) theory.}

\textit{The atmosphere of the Sun is multi-layered. Starting in the lowest layer, known as
	the photosphere, and moving up through the chromosphere and transition region we
	reach the upper atmosphere, known as the corona. The solar atmosphere, particularly
	the corona, is dominated by a complex and dynamic magnetic field that makes it
	highly inhomogeneous. This gives rise to many high-energy events such as jets,
	eruptions, and flares. These dynamic solar events, amongst other things, drive MHD
	1waves in the solar atmosphere which can be guided by the inhomogeneous magnetic
	field. MHD waves are similar to waves in terrestrial fluids, such as sound waves in
	air, but as well as a pressure gradient restoring force, MHD waves owe their existence
	to a restoring force due to perturbations of the magnetic field. MHD waves whose
	restoring force is a combination of the pressure gradient and this magnetic force, but
	not other forces such as gravity and Coriolis, are known as magneto-acoustic waves.}

\textit{MHD waves in the Sun can be used to approximate plasma parameters, such as
	the magnetic field strength, that are difficult to measure using traditional methods
	(Nakariakov and Verwichte, 2005; De Moortel and Nakariakov, 2012). This is done
	by comparing observations of MHD waves in the solar atmosphere to theoretical results from studying MHD wave propagation in waveguides that approximate those
	in the solar atmosphere, formed by a complex structuring of the magnetic field. This
	technique, known as solar magneto-seismology, has been an emerging field over the
	last few decades, and is on track to become a key tool for solar physics as the next
	generation of solar telescopes with greater spatial and temporal resolution are developed. The significance of making good approximations of plasma parameters in the
	solar atmosphere is so that we can use realistic parameters in numerical simulations
	and to gain an understanding of what conditions lead to instability and thus leading
	to solar flares and coronal mass ejections, which pose a significant threat to modern
	society on Earth (Cabinet Office, 2015).}



\subsection{Solar plasma}
Plasma - a quasineutral gas of
charged particles
exhibiting
collective
behaviour.
$>99$ percent of baryonic
matter in universe
is in plasma state.
Plasmas create
magnetic fields
and interact with
magnetic fields.

%------------------------------------------------------------------------------
\section{Magnetohydrodynamics}
\label{sec: MHD}
%------------------------------------------------------------------------------

\subsection{The equations of ideal magnetohydrodynamics} \label{sec: MHD eqns}

\textcolor{red}{To do: include charge neutrality? Single fluid? More discussion of amperes equation and the non-relativistic assumption?}

To build up a mathematical description of the Sun's plasma dynamics, let's motivate some assumptions.

The Sun's plasma, just like all matter in the Universe, is made up of particles\footnote{atoms or subatomic particles, depending on the temperature of its location in the Sun}, but the phenomena such as MHD waves that we are concerned with in this Thesis operate on a \textit{macroscopic} level. By this we mean on length-scales much larger than the \textit{mean free path}\footnote{Approximately 1 cm - 1 km in the Sun. \textcolor{red}{REFERENCE}}. This means that the \textit{Knudsen number}, the dimensionless parameter defined by the ratio of the mean free path to a characteristic length scale, in the Sun is much less than unity. This motivates the \textbf{continuum assumption}, where the fluid is considered to ``fill up" the space in which is is contained, so that small-scale inhomogeneities caused by particle dynamics are negligible. This gives us a coherent notion of fluid velocity, $\mathbf{v}(\mathbf{x}, t) = (v_1(\mathbf{x}, t), v_2(\mathbf{x}, t), v_3(\mathbf{x}, t))$, density, $\rho(\mathbf{x}, t)$, and pressure, $p(\mathbf{x}, t)$, as functions of continuous position, $\mathbf{x}$, and time, $t$.

The universe gifts us fundamental laws that are obeyed by all classical mechanics systems upon which we can build our framework. Firstly, the \textbf{conservation of mass} tells us that the change in density in a fixed volume is due only to mass entering or leaving the volume. The rate of change of density in a fixed volume $V$ is
\begin{equation}
	\frac{d}{dt} \iiint_V \rho ~d\mathbf{x} = \iiint_V \frac{\partial\rho}{\partial t} ~d\mathbf{x} \label{cont der 1}
\end{equation}
and the rate of mass flux into this volume, whose bounding surface we denote by $S$, which has infinitesimal surface normal component $d\mathbf{s}$, is
\begin{equation}
	-\iint_S \rho \mathbf{v} ~d\mathbf{s} = \iiint_V -\nabla\cdot(\rho\mathbf{v}) ~d\mathbf{x}, \label{cont der 2}
\end{equation}
by use of the divergence theorem. Equations~\eqref{cont der 1} and~\eqref{cont der 2} must be equal for any volume $V$ so the integrands must be equal, that is
\begin{equation}
	\frac{\partial\rho}{\partial t} + \nabla\cdot(\rho \bv) = 0, \label{cont eqn}
\end{equation}
known as the \textbf{continuity equation}.

Secondly, the \textbf{conservation of momentum} tells us that the momentum in a volume $V$ that moves with the fluid is only changed by forces exerted on the fluid. The rate of change of momentum in this volume is
\begin{equation}
	\frac{d}{dt} \iiint_V \rho\bv ~d\mathbf{x} = \iiint_V \rho\frac{D\bv}{Dt} ~d\mathbf{x}, \label{mom der 1}
\end{equation}
where $D/Dt = \partial/\partial t + \bv\cdot\nabla$ is derivative observed when moving with the fluid, known as the \textit{material derivative}. The forces acting upon the fluid are either \textit{surface forces} (such as pressure gradient force and viscosity) that act on an internal or external surface, or \textit{body forces}, $\mathbf{b}$, (such as gravity and magnetic forces) that act on the whole volume. The surface forces form a stress tensor $\sigma$, so that the total force exerted on a volume of fluid is
\begin{equation}
	\iint_S \sigma\cdot d\mathbf{s} + \iiint_V \mathbf{b} ~d\mathbf{x} = \iiint_V (\nabla\cdot \sigma + \mathbf{b}) ~d\mathbf{x}, \label{mom der 2}
\end{equation}
using the divergence theorem. Equations~\eqref{mom der 1} and~\eqref{mom der 2} must be equal for any volume $V$ so the integrands must be equal, that is
\begin{equation}
\rho\frac{D\bv}{Dt} = \nabla\cdot \sigma + \mathbf{b}. \label{mom der 3}
\end{equation}
Motivated by the large role they play in the dynamics of small to medium scale solar phenomena, in this Thesis we focus on the effects of magnetic forces and neglect commonly used other forces such as gravity and viscosity. Denoting the magnetic field and permeability by $\mathbf{B}$ and $\mu$, respectively, the magnetic force felt by a (non-relativistic) fluid element is $(\nabla\times\mathbf{B})\times\mathbf{B}/\mu$. By neglecting viscosity, we can write the stress tensor as $\sigma = -pI$, where $I$ is the $3\times3$ identity matrix. This reduces Equation\eqref{mom der 3} to the \textbf{momentum equation}, namely
\begin{equation}
\rho\frac{D\bv}{Dt} = -\nabla p + \frac{1}{\mu}(\nabla\times\mathbf{B})\times\mathbf{B}. \label{mom eqn}
\end{equation}

Finally, \textbf{conservation of entropy} occurs during processes that are \textit{adiabatic} and \textit{reversible}. The entropy per unit mass, $s$, for an \textit{ideal fluid} is given by
\begin{equation}
	s = C_v\ln\left(\frac{p}{\rho^\gamma}\right) + const, \label{entropy}
\end{equation}
where $C_v$ and $\gamma$ are the specific heat at constant volume and the adiabatic index, respectively. Entropy is conserved when moving with the fluid, which, using Equation~\eqref{entropy}, can be written in the form
\begin{equation}
\frac{D}{Dt}\left(\frac{p}{\rho^\gamma}\right) = 0, \label{energy eqn}
\end{equation}
which we call the \textbf{energy equation} because it can also be interpreted as the fundamental law of conservation of energy.

Equations~\eqref{cont eqn}, \eqref{energy eqn}, and the three components of \eqref{mom eqn} are a system of five equations that relate eight unknowns ($\rho, p$, and three components of $\bv$ and $\bB$). Three additional equations are required to close the system. To establish these additional equations, we use \textbf{Ohm's Law}, which asserts that the current density, $\mathbf{j}$ is proportional to the total electric field when moving with the fluid,
\begin{equation}
	\mathbf{j} = \frac{1}{\eta}(\mathbf{E} + \bv\times\bB),
\end{equation}
where $\mathbf{E}$ is the electric field. In this Thesis, we are concerned with plasmas where resistive effects, including magnetic reconnection and diffusion, are unimportant. Therefore, we can neglect the left hand side of this equation to give
\begin{equation}
\mathbf{E} + \bv\times\bB = 0. \label{ohms law}
\end{equation}
\textbf{Faraday's law} of electromagnetism relates the gradient of the electric field to the change in magnetic field:
\begin{equation}
	\nabla\times\mathbf{E} = -\frac{\partial\bB}{\partial t}. \label{faraday eqn}
\end{equation}
Combining Equations~\eqref{ohms law} and~\eqref{faraday eqn} gives us the \textbf{induction equation} (for an ideal plasma)
\begin{equation}
	\frac{\partial\bB}{\partial t} = \nabla\times(\bv\times\bB). \label{ind eqn}
\end{equation}
Equations~\eqref{cont eqn}, \eqref{mom eqn}, \eqref{energy eqn}, and \eqref{ind eqn} constitute a complete set of equations that describe the evolution of an \textit{ideal plasma} and are known as the \textbf{ideal MHD equations}.

In addition, \textbf{Gauss' Law}, which states that $\nabla\cdot\bB = 0$, puts a constraint on the choice of initial magnetic field. Integrating Equation~\eqref{ind eqn} shows us that initial satisfaction of Gauss' Law ensures its satisfaction for all later time.


\subsection{Ideal magnetohydrodynamic behaviour}
The ideal plasma assumption approximates the plasma to be perfectly conducting. Ideal plasmas behave in unique and surprisingly simple ways that will be discussed in this subsection. We will briefly discuss the decomposition of the Lorentz force into magnetic tension and pressure, the conservation of magnetic flux, and the conservation of magnetic field lines.

In this discussion it is helpful to define the notion of a \textit{magnetic field line}. Magnetic field lines, or just ``field lines", are lines parallel to the magnetic field, $\bB$. The local strength of the magnetic field is proportional to the local field line density. Magnetic field lines are fictitious and are conceived of merely for ease of understanding and visualisation.


\subsubsection{Magnetic tension and pressure}
The Lorentz force in the momentum Equation~\eqref{mom eqn} can be decomposed as
\begin{equation}
	\frac{1}{\mu}(\nabla\times\bB)\times\bB = \frac{1}{\mu}(\bB\cdot\nabla)\bB - \nabla\left(\frac{\bB^2}{2\mu}\right).
\end{equation}
The first term on the right hand side is the \textit{magnetic tension} force which acts normal to $\bB$. It acts to ``straighten out" magnetic field lines and it's strength is proportional ot the field line's curvature. The second term on the right hand side is the \textit{magnetic pressure} force which acts along any negative gradient in magnetic field strength. It acts to ``spread out" magnetic field lines.


\subsubsection{Magnetic flux conservation}
The magnetic flux through a surface $S$ bounded by a simple closed curve $C$ is
\begin{equation}
	\Psi = \iint_S \bB\cdot d\mathbf{s}.
\end{equation}
The magnetic flux can change in two ways: when the magnetic field $\bB$ changes with $S$ held fixed, and the flux swept out by the $C$ as it moved with the plasma. Combining these, the rate of change of flux is
\begin{equation}
	\frac{d \Psi}{dt} = \iint_S \frac{\partial\bB}{\partial t}\cdot d\mathbf{s} + \oint_C \bB\cdot \bv \times d\mathbf{l},
\end{equation}
where $d\mathbf{l}$ is an element parallel to curve $C$. Using Stokes' Theorem on the second term on the right hand side, the above equation becomes
\begin{equation}
\frac{d \Psi}{dt} = \iint_S \left[ \frac{\partial\bB}{\partial t} - \nabla\times(\bv\times\bB) \right] \cdot d\mathbf{s} = 0,
\end{equation}
using Equation~\eqref{ind eqn}. Therefore, magnetic flux is conserved in an ideal plasma.

This result has the important corollary that the plasma and the magnetic field lines are ``frozen in". That is, wherever the magnetic field moves, the plasma follows, and \textit{vice versa}. In other words, plasma elements that initially occupy the same field line will always do so. This is known as \textbf{Alfv\'{e}n's frozen flux theorem}.


%------------------------------------------------------------------------------
\section{Waves in the solar atmosphere}
\label{sec: waves}
%------------------------------------------------------------------------------

\subsection{Magnetohydrodynamic waves in homogeneous plasma}
Whilst the Sun's inhomogeneity is undeniable, it is instructive to first study the MHD waves that propagate in a homogeneous plasma. We start with the ideal MHD equations derived in Section~\ref{sec: MHD eqns}
\begin{align}
	\frac{\partial\rho}{\partial t} + \nabla\cdot(\rho \bv) &= 0, \\
	\rho\frac{D\bv}{Dt} &= -\nabla p + \frac{1}{\mu}(\nabla\times\mathbf{B})\times\mathbf{B}, \\
	\frac{D}{Dt}\left(\frac{p}{\rho^\gamma}\right) &= 0, \\
	\frac{\partial\bB}{\partial t} &= \nabla\times(\bv\times\bB).
\end{align}
The complexity of these equations is due to their non-linearity. Consider a stationary homogeneous plasma with equilibrium magnetic field given by $\mathbf{B_0} = (0, 0, B_0)$, without loss of generality. Each parameter can be written as a sum of its equilibrium quantity and a perturbation from that equilibrium, namely, $f = f_0 + f'$, where $f$ is a placeholder for parameters $\rho, p, \bv$, and $\bB$. The equilibrium plasma is stationary and homogeneous, so $\bv_0 = 0$, and each equilibrium parameter is uniform in space. By considering just small perturbations from equilibrium, \textit{i.e.} $f' \ll f_0$ for each parameter, we can remove the non-linearity from the governing equations. Substituting this form of the parameters into the ideal MHD equations and neglecting terms of quadratic order in small perturbation parameters gives us the linearised ideal MHD equations
\begin{align}
	\frac{\partial\rho'}{\partial t} + \rho_0(\nabla\cdot\bv') &= 0, \label{cont eqn lin} \\
	\rho_0\frac{\partial\bv'}{\partial t} &= -\nabla p' + \frac{1}{\mu}(\nabla\times\bB')\times\bB_0, \label{mom eqn lin} \\
	\frac{\partial p'}{\partial t} - c_0^2\frac{\partial\rho'}{\partial t} &= 0, \label{energy eqn lin} \\
	\frac{\partial\bB'}{\partial t} &= \nabla\times(\bv'\times\bB_0), \label{ind eqn lin}
\end{align}
where $c_0 = \sqrt{\gamma p_0/\rho_0}$ is the \textit{sound speed}. This system of equations can be combined into the generalised wave equation
\begin{equation}
	\frac{\partial^2\bv}{\partial t^2} = c_0^2\nabla(\nabla\cdot\bv) + \frac{1}{\mu\rho_0}(\nabla\times(\nabla\times(\bv\times\bB_0)))\times\bB_0, \label{homogeneous wave eqn}
\end{equation}
where we have dropped the apostrophe on $\bv'$ for brevity. The form of this equation motivates a search for solutions of the form
\begin{equation}
	\bv(\mathbf{x}, t) = \hat{\bv}e^{i(\mathbf{k}\cdot\mathbf{x} - \omega t)},
\end{equation}
corresponding to \textit{plane-waves} with wavenumber vector $\mathbf{k}$, circular frequency $\omega$, and amplitude $\hat{\bv}$ that is spatially independent. This reduces Equation~\eqref{homogeneous wave eqn} to an eigenvalue problem with eigenfrequency $\omega^2$, namely
\begin{equation}
	\omega^2\hat{\bv} = c_0^2\mathbf{k}(\mathbf{k}\cdot\hat{\bv}) + \frac{1}{\mu\rho_0}(\mathbf{k}\times(\mathbf{k}\times(\hat{\bv}\times\bB_0)))\times\bB_0. \label{homogeneous wave eqn 2}
\end{equation}

With the aim of first studying a limiting solution, the ratio of the first term to the second term on the right hand side fo the above equation is
\begin{equation}
	\frac{|c_0^2\mathbf{k}(\mathbf{k}\cdot\hat{\bv})|}{|\frac{1}{\mu\rho_0}(\mathbf{k}\times(\mathbf{k}\times(\hat{\bv}\times\bB_0)))\times\bB_0|} = \frac{c_0^2}{v_A^2},
\end{equation}
where $v_A = B_0/\sqrt{\mu\rho_0}$ is the \textit{Alfv\'{e}n speed}.

When the sound speed dominates the Alfv\'{e}n speed\footnote{This is known as the \textit{high beta limit}. Here, beta refers to the plasma beta parameter defined as the ratio of kinetic pressure to magnetic pressure and can be written as $\beta = \frac{2c_0^2}{\gamma v_A^2}$}, and assuming that $\mathbf{k}\cdot\hat{\bv} \neq 0$ so that the fluid is compressible, taking the dot product of $\mathbf{k}$ and Equation~\eqref{homogeneous wave eqn 2} leads to $\omega = \pm kc_0$. These solutions correspond to forwards and backwards propagating \textit{sound waves}. They are longitudinal waves that propagate isotropically in a homogeneous fluid.

When neither the sound speed or Alfv\'{e}n speed dominates, we can write Equation~\eqref{homogeneous wave eqn 2} in component form as
\begin{equation}
	\left(\begin{matrix}
		\omega^2 - k_x^2c_0^2 - (k_x^2 + k_z^2)v_A^2 & 0 & -k_x^2k_z^2c_0^2 \\
		0 & \omega^2 - k_z^2v_A^2 & 0 \\
		-k_xk_zc_0^2 & 0 & \omega^2 - k_z^2c_0^2
	\end{matrix}\right)
	\left(\begin{matrix}
		\hat{v}_x \\
		\hat{v}_y \\
		\hat{v}_z
	\end{matrix} \right) = 0,
\end{equation}
where, without loss of generality, we have let $\mathbf{k} = (k_x, 0, k_z)$. For there to exist non-trivial solutions to this equation, the determinant of the matrix must vanish, that is
\begin{equation}
	(\omega^2 - k_z^2v_A^2)\left[\omega^4 - \omega^2k^2(c_0^2 + v_A^2) + k^2k_z^2c_0^2v_A^2 \right] = 0, \label{det sol}
\end{equation}
where we have defined $k^2 = k_x^2 + k_z^2$.

The first set of solutions to Equation~\eqref{det sol} are $\omega = \pm k_zv_A$. These solutions correspond to forward and backwards propagating \textit{Alfv\'{e}n waves}. They are transverse oscillations of the magnetic field that propagate parallel to the magnetic field. They are described as purely magnetic waves because they are not associated with density perturbation.

The second set of solutions to Equation~\eqref{det sol} are
\begin{equation}
	\omega^2 = \frac{1}{2}k^2(c_0^2 + v_A^2)\left(1 \pm \sqrt{1 - 4c_T^2\frac{k_z^2}{k^2}}\right),
\end{equation}
where $c_T = c_0^2v_A^2/\sqrt{c_0^2 + v_A^2}$ is the \textit{tube speed}, so called because it is the phase speed of slow waves in a thin magnetic flux tube (see Section~\ref{sec: MHD waves tube}). These solutions correspond \textit{magnetoacoustic waves}, which are oscillations restored by a combination of both the pressure gradient and Lorentz forces. The solutions with the higher frequency (and hence faster phase speed) are known as \textit{fast magnetoacoustic waves} and the solutions with the lower frequency are known as \textit{slow magnetoacoustic waves}. Physically, perturbations in the fast mode are restored by the pressure gradient and Lorentz forces working in phase, whereas perturbations in the slow mode are restored by the forces working in anti-phase, leading to a less strong restoring force for slow modes.


\subsection{Magnetohydrodynamic waves in inhomogeneous plasma}
The Sun's atmosphere is far from homogeneous. To progress towards an understanding of MHD waves in the solar atmosphere, we must study MHD waves in simple inhomogeneous plasma.

In this subsection, we review the linear MHD waves along simple inhomogeneous structures: a tangential interface (Section~\ref{sec: MHD waves interface}), a symmetric slab (Section~\ref{sec: MHD waves sym slab}), and a magnetic flux tube (Section~\ref{sec: MHD waves tube}).

\text{red}{Consider adding a figure showing an interface, slab, and tube.}


\subsubsection{Tangential interface} \label{sec: MHD waves interface}

\subsubsection{Symmetric slab} \label{sec: MHD waves sym slab}

\subsubsection{Magnetic flux tube} \label{sec: MHD waves tube}

%------------------------------------------------------------------------------
\section{Thesis outline}
\label{sec:outline}
%------------------------------------------------------------------------------


\bibliographystyle{plainnat}
\bibliography{references}  

\end{document}
